\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{amsmath}
\usepackage{multicol}

\usepackage[hmargin=3cm,vmargin=6.0cm]{geometry}
%\topmargin=0cm
\topmargin=-2cm
\addtolength{\textheight}{6.5cm}
\addtolength{\textwidth}{2.0cm}
%\setlength{\leftmargin}{-5cm}
\setlength{\oddsidemargin}{0.0cm}
\setlength{\evensidemargin}{0.0cm}

%misc libraries goes here

\begin{document}

\section*{Student Information } 
%Write your full name and id number between the colon and newline
%Put one empty space character after colon and before newline
Full Name :  Alperen OVAK \\
Id Number :  2580801\\

% Write your answers below the section tags
\section*{Answer 1}

\subsection*{a)} 

Given that the sample standard deviation (s) is not provided, we'll use the guaranteed standard deviation of the measurement device, which is $\sigma$ = 2.7.

The formula to calculate the confidence interval for the population mean is:

\[ \bar{x} \pm z \times \frac{\sigma}{\sqrt{n}} \]

\begin{itemize}
    \item $\bar{x}$ is the sample mean,
    \item $z$ is the z-score corresponding to the desired confidence level (95\% in this case),
    \item $\sigma$ is the population standard deviation,
    \item $n$ is the sample size.
\end{itemize}

First, let's calculate the sample mean (\(\bar{x}\)) and the z-score for 95% confidence interval.

Given sample measurements:
\[ x = [6.4, 9.5, 8.2, 10.2, 7.6, 11.1, 8.7, 7.3, 9.1] \]

\[ \bar{x} = \frac{6.4 + 9.5 + 8.2 + 10.2 + 7.6 + 11.1 + 8.7 + 7.3 + 9.1}{9} = 8.67 \]

Now, to find the z-score for a 95\% confidence interval, we consult the standard normal distribution table or our book:

For a 95\% confidence interval, we need to find the z-score. Since this "Two-sided Z-test", we should find the value of $z_{\frac{\alpha}{2}}$ which is $z_{0.025}$, so the z-score is approximately 1.960 from Chapter 9.2.1.

Substituting the values into the formula:

\[ \text{Lower bound} = 8.67 - 1.960 \times \frac{2.7}{\sqrt{9}} \]

\[ \text{Lower bound} \approx 6.906 \]

\[ \text{Upper bound} = 8.67 + 1.960 \times \frac{2.7}{\sqrt{9}} \]

\[ \text{Upper bound} \approx 10.434 \]

So, the 95\% confidence interval for the population mean is approximately (6.906, 10.434).

\subsection*{b)} 

To determine the sample size required for a specific margin, we can analyze the margin formula:

\[ {E} = \frac{z \times \sigma}{\sqrt{n}}\]

In our case we want to set a limit, s.t:

\[ {1.25} \geq \frac{z \times \sigma}{\sqrt{n}}\]

we can get the formula easily to find boundary of $n$:

\[ n \geq \left( \frac{z \times \sigma}{1.25} \right)^2 \]

Now let's solve the equation:

Know that \(z = 1.96\) for a 95\% confidence interval, and \(\sigma = 2.7\), substituting the values:

\[ n \geq \left( \frac{1.96 \times 2.7}{1.25} \right)^2 \]

\[ n \geq \left( \frac{5.292}{1.25} \right)^2 \]

\[ n \geq \left( 4.2336 \right)^2 \]

\[ n \geq 17.93 \]

Rounding up, the sample size required $n$ is approximately 18 to achieve a margin of error of 1.25 units with a 95\% confidence level.

\section*{Answer 2}

\subsection*{a)} 

In hypothesis testing, the null hypothesis (\(H_0\)) typically claims that there is no effect or no change, while the alternative hypothesis (\(H_1\) or \(H_a\)) represents the claim that the researcher is trying to find evidence for.

Leyla and Mecnun discuss about whether there has been a change in the average monthly revenue compared to last year, we can define the hypotheses as follows:

In this scenario, Mecnun's claim, which asserts that the revenue has remained the same, should be considered as the null hypothesis (\(H_0\)), while Leyla's claim, suggesting that the revenue has increased, becomes the alternative hypothesis (\(H_1\)).

\subsection*{b)} 

To test Mecnun's claim that the average monthly revenue has remained the same compared to last year at a 5\% level 
of significance, we can run a hypothesis test using the sample data collected this year.

We know that: 
\begin{itemize}
    \item Last year's average monthly revenue: $\mu_0 = 20,000$ TL
    \item Standard deviation last year: $\sigma = 3,000$ TL
    \item Sample size: $n = 50$
    \item Sample mean: $\bar{x} = 22,000$ TL
\end{itemize}

We'll perform a z-test because we have the population standard deviation (\(\sigma\)) and the sample size is relatively large (n \(>\) 30).

The formula for the z-score is given by:

\[ z = \frac{\bar{x} - \mu_0}{\frac{\sigma}{\sqrt{n}}} \]

Substituting the given values:

\[ z = \frac{22,000 - 20,000}{\frac{3,000}{\sqrt{50}}} \]

\[ z = \frac{2,000}{\frac{3,000}{\sqrt{50}}} \]

\[ z \approx 4.714 \]

Now, we compare the calculated z-score with the critical z-value at a 5\% level of significance.

For a one-sided right tail test at $\alpha$ = 0.05, the critical z-value is approximately 1.645.

Since our calculated z-score (4.714) is much greater than the critical z-value (1.645), we reject the null hypothesis.

Therefore, we have enough evidence to conclude that Mecnun's claim is not supported at the 5\% level of significance. The average monthly revenue this year is significantly different from last year, indicating that there has been a change.

\subsection*{c)} 

To calculate the p-value for Mecnun's test, we can use the z-score we obtained earlier, which is approximately \(z = 4.714\).

The p-value is the probability of observing a test statistic as extreme as, or more extreme than, the one observed, under the assumption that the null hypothesis is true.

For a right-tailed test, the p-value is the area under the standard normal distribution curve to the right of the calculated z-score.

The equation of p for right sided case is:

\[P =(Z \geq Z_{obs}) = P(Z \geq 4.714) = 1 - \phi(4.714)\]

\[\approx 0\]


In this case, our p-value is really small, almost zero. This suggests that it's highly unlikely to see an average monthly revenue of 
22,000 TL or more, assuming the usual average is 20,000 TL. So, Mecnun's data strongly suggests that things have changed, supporting Leyla's claim that the monthly revenue has gone up compared to last year.

In conclusion, Mecnun's p-value is close to zero, providing strong evidence to reject the null hypothesis in favor of the alternative hypothesis, supporting Leyla's claim that the average monthly revenue has increased compared to last year.

\subsection*{d)} 

To compare the average monthly revenue of their store to that of the competitor's store, they can conduct a two-sample z-test for the mean, as they have the population parameters. 

The formula for the z-test statistic for two samples is:

\[ Z = \frac{\bar{x}_1 - \bar{x}_2}{\sqrt{\frac{\sigma_1^2}{n_1} + \frac{\sigma_2^2}{n_2}}} \]

Where:
\begin{itemize}
    \item $\bar{x}_1$ and $\bar{x}_2$ are the sample means (base store: 22,000 TL, competitor's store: 24,000 TL)
    \item $\sigma_1$ and $\sigma_2$ are the population standard deviations (base store: 3,000 TL, competitor's store: 4,000 TL)
    \item $n_1$ and $n_2$ are the sample sizes (base store: 50, competitor's store: 40)
\end{itemize}


First, let's calculate the z-score:

\[ Z = \frac{22000 - 24000}{\sqrt{\frac{3000^2}{50} + \frac{4000^2}{40}}} \]

\[ Z = \frac{-2000}{\sqrt{\frac{9000000}{50} + \frac{16000000}{40}}} \]

\[ Z = \frac{-2000}{\sqrt{180000 + 400000}} \]

\[ Z = \frac{-2000}{\sqrt{580000}} \]

\[ Z \approx \frac{-2000}{761.577} \]

\[ Z \approx -2.626 \]

Now, we compare the calculated z-score with the critical z-value at a 1\% level of significance.

For a one-sided right tail test at $\alpha$ = 0.01, the critical z-value is approximately 2.326.

Since the calculated z-score (-2.626) is less than the critical z-value (2.326), we fail to reject the null hypothesis. Therefore, at a 1\% level of significance, there is not enough evidence to claim that the average monthly revenue of their store is higher than that of the competitor's store.

\section*{Answer 3}


To determine if there is a significant association between gender and coffee preference, we can use the chi-square test of independence. This test evaluates whether there is a relationship between two categorical variables. In this case, the variables are gender (male or female) and coffee preference (black coffee, coffee with milk, or coffee with sugar).

The null hypothesis (H0) is that there is no association between gender and coffee preference, while the alternative hypothesis (H1) is that there is an association between them.

Let's calculate the expected counts:

\begin{multicols}{3}
    \noindent
    \[ \widehat{\text{Exp}}(1,1) = \frac{(69)(100)}{(200)} = 34.5 \]
    \[ \widehat{\text{Exp}}(1,2) = \frac{(69)(100)}{(200)} = 34.5 \]
    \[ \widehat{\text{Exp}}(1,3) = \frac{(79)(100)}{(200)} = 39.5\]
    \[ \widehat{\text{Exp}}(2,1) = \frac{(79)(100)}{(200)} = 39.5\]
    \[ \widehat{\text{Exp}}(2,2) = \frac{(52)(100)}{(200)} = 26 \]
    \[ \widehat{\text{Exp}}(2,3) = \frac{(52)(100)}{(200)} = 26 \]
\end{multicols}

So, the table of expected counts:

% Expected Frequencies
\[
\begin{array}{|c|c|c|c|}
\hline
& \text{Black Coffee} & \text{Coffee with Milk} & \text{Coffee with Sugar} \\
\hline
\text{Male Respondents} & 34.5 & 39.5 & 26 \\
\text{Female Respondents} & 34.5 & 39.5 & 26 \\
\hline
\text{Row Total} & 69 & 79 & 52 \\
\hline
\end{array}
\]

The chi-square statistic ($\chi^2$) can be calculated as follows:

\[
\chi^2 = \sum \frac{(O - E)^2}{E}
\]

The chi-square value is:
\[
\chi^2 =  \frac{(52 - 34.5)^2}{34.5} + \frac{(17 - 34.5)^2}{34.5} + \frac{(16 - 39.5)^2}{39.5}+\frac{(63 - 39.5)^2}{39.5}+\frac{(32 - 26)^2}{26}+\frac{(20 - 26)^2}{26}
\]

\[
\chi^2 \approx 48,5  
\]

Now, Let's calculate the degrees of freedom using the formula \( (\text{Rows} - 1) \times (\text{Columns} - 1) \).

Given that there are 2 rows (Male and Female) and 3 columns (Black Coffee, Coffee with Milk, Coffee with Sugar), the degrees of freedom would be \( (2 - 1) \times (3 - 1) = 2 \).

From Table A6 with d.f., we can see that the P-value $P < 0.001$. 

We know that when the calculated chi-square statistic exceeds the critical value, it suggests that the observed frequencies are significantly different from the expected frequencies, and the null hypothesis is rejected.
Therefore, we can conclude that there is a significant association between gender and coffee preference based on the results of the chi-square test.

\end{document}
