\pagenumbering{arabic}

\chapter{Introduction} \label{introduction}


This Software Architecture Description (SAD) for the Koster Seafloor Observatory (KSO) is written in accordance with ISO/IEC/IEEE~42010:2011 \cite{iso29148} and adopts viewpoints from Rozanski \& Woods’ \emph{A Viewpoint Catalog} \cite{RW} to structure four principal views—Functional, Information, Development, and Deployment—each addressing specific stakeholder concerns and quality‐attribute trade‐offs.

\section{Purpose and objectives of \gls{kso}}

The KSO system integrates video data management, citizen‐science annotation, and machine‐learning inference to accelerate marine‐biodiversity research. Its primary objectives are to:
\begin{itemize}
  \item Ingest and archive ROV/AUV subsea movies in a scalable hot/cold storage architecture.
  \item Enable citizen scientists to classify clips and draw bounding‐box annotations via an intuitive web interface, aggregating results through consensus algorithms.
  \item Train and serve deep‐learning models (e.g., \gls{yolov3}) for automated object detection, exposing them through a \gls{restapi} and interactive dashboard. \cite{anton2021kso}
  \item Visualize and export ecological metrics—species counts, distributions, and trends—to standard formats for downstream analysis.
  \item Maintain openness and extensibility, providing modular code, clear documentation, and integration points for new workflows or models.
\end{itemize}

\section{Scope}

\paragraph{In scope}
\begin{itemize}
  \item \textbf{Data Management Module}: Video segmentation, metadata extraction (Darwin Core–compliant), SQLite/PostgreSQL storage, backup and archival pipelines.
  \item \textbf{Citizen‐Science Module}: Two Zooniverse workflows (clip classification, frame annotation), tutorial management, aggregation thresholds, and export utilities.
  \item \textbf{Machine‐Learning Module}: Preprocessing (background correction, augmentation), model training/validation on \gls{gpu} cluster, hyperparameter tuning, RESTful inference service, and Streamlit‐based visualization.
  \item \textbf{User Interfaces}: Web portal for annotation, dashboard for model performance metrics and data exports.
\end{itemize}
\paragraph{Out of scope}
\begin{itemize}
  \item \gls{rov}/\gls{auv} mission planning or vehicle control.
  \item Expert taxonomic curation beyond automated \gls{qc} thresholds.
  \item Non-video oceanographic data types (e.g., acoustic, chemical).
  \item Third‐party archival systems beyond the KSO server infrastructure.
\end{itemize}

\section{Stakeholders and their concerns}
\begin{table}[ht]
    \small
    \centering
    \begin{tabular}{p{0.25\textwidth} p{0.70\textwidth}}
      \toprule
      \textbf{Stakeholder} & \textbf{Concerns \& Usage of \gls{sad} Views} \\
      \midrule
      Marine Ecologists &
        \begin{itemize}[nosep,leftmargin=*]
          \item Verify data accuracy and species coverage (Information view)
          \item Explore spatial/temporal visualizations (Functional \& Deployment views)
        \end{itemize} \\
      \addlinespace
      Citizen Scientists &
        \begin{itemize}[nosep,leftmargin=*]
          \item Understand annotation workflow and UI components (Functional view)
          \item Track progress and consensus rules (Information view)
        \end{itemize} \\
      \addlinespace
      \gls{ml} Engineers \& Developers &
        \begin{itemize}[nosep,leftmargin=*]
          \item Inspect component interactions and dataflows for preprocessing, training, and inference (Functional \& Information views)
          \item Manage code modules and dependencies (Development view)
        \end{itemize} \\
      \addlinespace
      System Administrators &
        \begin{itemize}[nosep,leftmargin=*]
          \item Plan deployment topology, storage allocation, and service‐to‐hardware mapping (Deployment view)
          \item Automate backups and scaling workflows (Development view)
        \end{itemize} \\
      \addlinespace
      Sponsors \& Funders &
        \begin{itemize}[nosep,leftmargin=*]
          \item Evaluate architectural extensibility and open‐source licensing (Development view)
          \item Assess risk‐reduction measures and trade‐off decisions (all views)
        \end{itemize} \\
      \bottomrule
    \end{tabular}
    \caption{Stakeholders and their primary concerns, mapped to SAD views.}
    \label{tab:stakeholders-concerns}
  \end{table}




